Intentional release of native species undermines ecological stability

### 2022-09-28 rmd/supporting_info.Rmd
Update supporting_info.Rmd

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

```{=tex}
\newpage
\pagenumbering{arabic}
```
# Methods

@@

## Table S3 Priors

Prior distributions used in the Bayesian models.

@@

knitr::kable(df_prior,
             format = "markdown")

@@

## Table S4 Parameter estimates of the Bayesian state-space model

Median estimates of the Bayesian state-space model. See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors. The parameter $\pmb{\phi}$ is a vector of prior scales ($\pmb{\phi}=2.5,...,2.5$). Site-specific parameters were excluded due to a large number of parameters.

@@

knitr::kable(df_ssm,
             align = c(rep("l", 2), rep("c", 2)),
             format = "markdown")

>>>>

---
output:
  bookdown::pdf_document2:
    number_sections: false
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
  - \pagestyle{fancy}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

```{=tex}
\newpage
\pagenumbering{arabic}
\def\figurename{Figure S\hspace{-.6ex}}
\def\tablename{Table S\hspace{-.6ex}}
```
# Methods

@@

## Priors

@@

knitr::kable(df_prior,
             format = "markdown",
             caption = "Prior distributions used in the Bayesian models. See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors. The parameter $\\pmb{\\phi}$ is a vector of prior scales ($\\pmb{\\phi}=2.5,...,2.5$).")

@@

## Parameter estimates of the Bayesian state-space model

@@

knitr::kable(df_ssm,
             align = c(rep("l", 2), rep("c", 2)),
             format = "markdown",
             caption = "Median estimates of the Bayesian state-space model. Site-specific parameters were excluded due to a large number of parameters.")
